Lit Review Figure

### 2018-07-18 code/Boot_Figure.Rmd
changing strategy from using plotly for all measures to shiny app filtering tasks

his is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4, width = 500)
```

### 2018-07-18 code/Lit_Review_Figure.Rmd
changing strategy from using plotly for all measures to shiny app filtering tasks

@@

Interactive plot

```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

Static plot

```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```

```{r warning=FALSE, message=FALSE}
fig_data = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
         raw1_fit0 = grepl('raw', variable_type),
         type = as.character(type)) %>%
  arrange(task_group, -raw1_fit0)
```

>>>>

```{r warning=FALSE, message=FALSE}
fig_data = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
         raw1_fit0 = grepl('raw', raw_fit),
         type = as.character(type)) %>%
  arrange(task_group, -raw1_fit0)
```

@@

# Interactive plot

```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '\n reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw(),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=F)
```

```{r warning=FALSE, message=FALSE, fig.height=72, echo=FALSE}
ggplotly(fig_data %>%
           mutate(dv = factor(dv, levels = dv[order(task)]),
                  days_cutoff = ifelse(days < 60, days, 120),
                  days = paste(days, '\n reference:', reference)) %>%
           filter(task == 'task') %>%
           ggplot(aes(y = var, x = retest_reliability, label=days))+
           geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#00BFC4')+
           facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
           theme(panel.spacing = unit(0.1, "lines"), 
                 strip.placement = "outside",
                 strip.text.y = element_text(angle=180),
                 panel.background = element_rect(fill = NA),
                 panel.grid.major = element_line(colour = "grey80")),
         tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=F)

# if you figure out how to make the panels for tasks and surveys separately you can use subplot() - a ggplotly function to plot them side by side
```

```{r message=FALSE, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '\n reference:', reference)) %>%
  filter(task_group == 'bis_bas_survey') %>%
  ggplot(aes(y = var, x = retest_reliability, label=days))+
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
  # facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  # facet_grid(task_group~.) +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'none')+
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3)),
  width=600)

```

# Static plot
